Post-replication citation patterns in psychology: Four case studies

### 2021-04-27 manuscript/manuscript.Rmd
Update manuscript.Rmd

We adopted a case study approach in order to develop a ‘narrow and deep’ understanding of the topic, as opposed to ‘broad and shallow’ approach, which would have required a deliberate representative sampling strategy. We chose these particular case studies because they involved prominent pre-registered multi-laboratory replication attempts with sample sizes between 23 - 211 times larger than the original studies, thus providing highly visible and highly credible evidence that strongly contradicted and outweighed earlier findings[^footnote3]. This facilitates additional interpretative clarity about the citation patterns one might expect to observe.

>>>>

We adopted a case study approach in order to develop a ‘narrow and deep’ understanding of the topic, as opposed to a ‘broad and shallow’ approach, which would have required a deliberate representative sampling strategy. We chose these particular case studies because they involved prominent pre-registered multi-laboratory replication attempts with sample sizes between 23 - 211 times larger than the original studies, thus providing highly visible and highly credible evidence that strongly contradicted and outweighed earlier findings[^footnote3]. This facilitates additional interpretative clarity about the citation patterns one might expect to observe.
